Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-03-21 acknowledgements/acknowledgements.tex
Updates from Overleaf

\begin{itemize}
\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis. Your expertise in MIR helped shape the direction of my research and make it a success. Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process. I also appreciate the time and effort you invested in mentoring me. Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
\vspace*{3mm}
\item My co-supervisor
\vspace*{3mm}
\item The Music Technology Group (MTG)
\vspace*{3mm}
\item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis. His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities. His guidance and advice on professional matters have been instrumental in my growth as a professional. I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
\vspace*{3mm}
Thank you all for being excellent advisors and playing a crucial role in completing my thesis. I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
\vspace*{3mm}
\item My family
\vspace*{3mm}
\item My girlfriend
\vspace*{3mm}
\end{itemize}

>>>>

\begin{itemize}
\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis. Your expertise in MIR, ML, and DSP helped shape the direction of my research and make it a success. Your unwavering support and encouragement helped me overcome any difficulties I encountered. I also appreciate the time and effort you invested in mentoring me. Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
\vspace*{3mm}
\item Cody Hesse and Sebastian Löf
\vspace*{3mm}
\item Epidemic Sound AB (\textit{Aktiebolag})
\vspace*{3mm}
\item My co-supervisor
\vspace*{3mm}
\item The Music Technology Group (MTG)
\vspace*{3mm}
\item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis. His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities. His guidance and advice on professional matters have been instrumental in my growth as a professional. I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
\vspace*{3mm}
Thank you all for being excellent advisors and playing a crucial role in completing my thesis. I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
\vspace*{3mm}
\item My family
\vspace*{3mm}
\item My girlfriend
\vspace*{3mm}
\end{itemize}

### 2023-03-21 introduction/Subsections/Objectives.tex
Updates from Overleaf

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
%POTENTIAL APPLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%

A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in Music Information Retrieval (MIR). Here are some examples:

\begin{enumerate}
\item Music recommendation: The learned embedding space can retrieve similar musical content and recommend songs or playlists to users based on their listening history or preferences.
\item Music classification: The embedding space can classify songs based on genre, mood, or other musical characteristics.
\item Music transcription: The learned embedding space can transcribe audio signals into symbolic music notation, such as MIDI or sheet music.
\item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
\item Music synchronization: The learned embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
\item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them
\end{enumerate}

### 2023-03-21 introduction/subsections/underlying language vs waveform.tex
Updates from Overleaf

At a high level, the underlying composition and the master recording represent different aspects of a musical work.

The underlying composition represents the musical and lyrical elements of the song in a fixed and notated form. It includes the melody, rhythm, and harmony of the song as well as the accompanying lyrics. The underlying composition is the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.

The master recording, on the other hand, is the tangible recording of the sound of the song. It captures the performance, production, and engineering aspects of the work. The master recording is the intellectual property of the performers, producers, or sound engineers, who have exclusive rights to reproduce, distribute, and prepare derivative works of the sound recording.

In essence, the underlying composition is a fixed and notated representation of the song's musical and lyrical elements, while the master recording is a tangible recording of the performance, production, and engineering aspects of the song. The underlying composition is owned by the songwriters, composers, musicians, or publishers, while the master recording is owned by the performers, producers, or sound engineers.

>>>>

The underlying composition and master recording represent distinct and essential aspects of a musical work. The underlying composition consists of the musical and lyrical elements of the song, including the melody, harmony, rhythm, and lyrics, which are fixed and notated forms of the musical work. The composition represents the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.

The master recording, on the other hand, is a tangible recording that captures the sound of the work's performance, production, and engineering aspects. The master recording is owned by the performers, producers, or sound engineers, who have exclusive rights to reproduce, distribute, and prepare derivative works of the sound recording.

In the scientific and technical realm, the underlying composition is considered a fixed, heuristic representation of the musical work, whereas the master recording represents the sound recording of the performance. The composition is typically notated, meaning the musical elements are represented by symbols representing specific pitches, rhythms, and chords. This notation provides a way to represent the musical work in a standardized form that can be read and interpreted by musicians and musicologists alike.

The master recording, on the other hand, is a physical recording that captures the sound of the work's performance, production, and engineering aspects. This recording represents a tangible artifact that can be played back and studied in detail to understand the nuances of the performance, such as the tempo, dynamics, and tonal quality. In addition, the master recording can be manipulated through various audio production techniques to create derivative works, such as remixes or cover versions of the original song.

Overall, the underlying composition and master recording represent two essential aspects of a musical work, each with unique characteristics, properties, and ownership rights. The composition represents the fixed musical and lyrical elements of the work. It is owned by songwriters, composers, musicians, or publishers. At the same time, the master recording captures the performance and production aspects of the work and is owned by the performers, producers, or sound engineers.
